Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-12-07 tex/scam/supple.tex
initial commit

\documentclass[12pt,pdftex,aos,noinfoline,addressasfootnote]{imsart}
%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}

\RequirePackage[OT1]{fontenc}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
\RequirePackage{hypernat}
\usepackage[ruled,section]{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{graphicx}
%\usepackage[hscale=0.7,vscale=0.8]{geometry}
\usepackage[text={6.0in,8.6in},centering]{geometry}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{yhmath}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{shadecolor}{gray}{0.9}
\definecolor{shadecolor}{gray}{0.9}
\hypersetup{citecolor=MidnightBlue}
\hypersetup{linkcolor=MidnightBlue}
\hypersetup{urlcolor=MidnightBlue}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{xr}
\externaldocument{main}

\renewcommand{\baselinestretch}{1.00}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

\input{macros}
\begin{document}

\begin{supplement}
%\sname{Supplement A}
\stitle{Supplement to Faithful Variable Screening for High-Dimensional Convex Regression}
\slink[doi]{doi}
\sdatatype{.pdf}
\sdescription{We provide detailed proofs of certain technical results,
together with further explanation of the Gaussian example
and simplifications when the density is a product.}
\end{supplement}

\section{Proofs of Technical Results}

@@

We restate Theorem~\ref{thm:deterministic} first for convenience. 
The following holds regardless of whether we impose the
$B$-boundedness condition  $\|f_k^*\|_\infty \leq B$
used in the consistency analysis.

@@

\bibliographystyle{imsart-nameyear}
\bibliography{local}

\end{document}

>>>>

\section{Supplement:  Proofs of Technical Results}

@@

We restate Theorem~\ref{thm:deterministic} first for convenience. 
The following holds regardless of whether we impose the $B$-boundedness condition (see discussion at the beginning of Section~\ref{sec:finitesample} for definition of the $B$-boundedness condition).

@@
